### 2019-03-30 7_conclusion.tex
New version of conclusion.

We presented Task Bench, a parameterized benchmark powerful enough to
enable the exploration of a broad space of application scenarios, but
also simple enough to permit implementation in a wide array of systems
to a level of quality sufficient for comparative study. Our study of
13 programming systems is novel in its breadth, as well as the depth
of insight it delivers about different systems. We discover, among
other things, that the baseline overhead of systems varies by up to 5
orders of magnitude.

Helping us in this endeavor is a new metric, minimum effective task
granularity (METG), which helps to sidestep a number of potential
issues in the evaluation of task scheduling performance, and helps to
separate such factors from changes in communication topology and
latency at increasing scales of the machine.

>>>>

Parameterized benchmarks are a promising new route for evaluating the
performance of parallel and distribute programming systems. By
composing a small number of orthogonal primitives, parameterized
benchmarks make it possible to explore a space of application
scenarios, while minimizing the marginal cost of developing each
additional feature. In this case of Task Bench, this has enabled a
comprehensive comparative study of programming system performance
which is unique in both the breadth of systems considered and the
depth of insight achieved about them.

Our study has both confirmed and challenged our intuitions. We have
found, unsurprisingly, that systems intended primarily for scientific
simulation are optimized for smaller task granularities than systems
for large-scale data analysis. The baseline overhead of these systems
spans over 5 orders of magnitude. Even among systems intended for HPC
there is easily 2 orders of magnitude in variation. The gap shrinks
with node count, as the most efficient systems are the most impacted
by increasing communication latencies, and also with numbers of
dependencies and with increasing task parallelism. In certain cases,
such as when task parallelism is available and compute is balanced
with communication, asynchronous systems show a substantial benefit.

Not considered in our analysis is the impact of programming system
features on programmer productivity and performance portability. Most
applications do not operate at the absolute extreme of runtime-limited
performance, and thus may choose to trade overhead for better
usability. Our study helps to quantify exactly how much a tradeoff is
being made, so that users can be better informed, and developers can
see the impact of features of the performance of their programming
systems.
